Errata

### 2025-04-08 tex/Results_Discussion.tex
Update dissertation files and bibliography references
- Modified Dissertation.tex to include additional packages for improved referencing and table formatting.
- Updated literatur.bib with corrected publisher information, added missing article details, and revised DOI links for accuracy.
- Enhanced table formatting in Manuscript-2.tex for clarity and consistency, including adjustments to statistical significance reporting.
- Revised section title in Results_Discussion.tex for consistency in manuscript numbering and formatting.
Update manuscript files with chapter marks and improve section form

\section{Effect of biocrust on soil aggregate stability (manuscript 1)}
\label{sec:BiocrustOnAggregateStability }

@@

\section{Effect of biocrust on water flow, erosion and nutrient flow (manuscript 2)}
\label{sec:BiocrustOnFlows}

@@

\section{Microbial, plant and moisture controls on soil structure and functionality (Manuscripts 3, 4 and 5)}
\label{sec:MicrobesPlantsMoistureStructure}

>>>>

\section[Effect of biocrust on soil aggregate stability]{Effect of biocrust on soil aggregate stability (manuscript 1)}
\label{sec:BiocrustOnAggregateStability }

@@

\section[Effect of biocrust on water flow, erosion and nutrient flow]{Effect of biocrust on water flow, erosion and nutrient flow (manuscript 2)}
\label{sec:BiocrustOnFlows}

@@

\section[Microbial, plant and moisture controls on soil structure and functionality]{Microbial, plant and moisture controls on soil structure and functionality (manuscripts 3, 4 and 5)}
\label{sec:MicrobesPlantsMoistureStructure}
